Thread Pool in GeckoDB/BOLSTER

### 2018-05-09 Presentations/Milestone2/presentation.tex
Second milestone presentation (without literature)

\section{Current Progress}

\section{Next Steps}

\section{Additional Literature Research}
    \begin{frame}
        \frametitle{Literature Research}
        \begin{itemize}
            \item 
        \end{itemize}
    \end{frame}

>>>>

\section{Current Progress}
\begin{frame}
	\frametitle{Current Progress}
	We...
	\begin{itemize}
		\item Implemented the lock free priority queue 
		\item Implemented the creation of threads and the assigning of tasks
		\item Added gtest framework to project and wrote tests for pool and queue
		\item Began first implementations of waiting for tasks to be finished
	\end{itemize}
\end{frame}

\section{Next Steps}
\begin{frame}
	\frametitle{Next Steps}
	We have to ...
	\begin{itemize}
		\item Find an efficient way ton wait for tasks
		\item Find an efficient way to idle threads until they get the next tasks
		\item Add metrics to threads and tasks and measure performance and overhead
		\item Add tests for all implementations
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Next Steps - Scheduling}
	Current approach:  
	\begin{itemize}
		\item Threads ask for next task in queue
	\end{itemize}
	Desired implementation: 
	\begin{itemize}
		\item Make own scheduling, assign tasks to threads
		\item Add possibility to try different scheduling approaches
		\item Measure thread idle and busy time for the approaches
	\end{itemize}
\end{frame}

\section{Additional Literature Research}
    \begin{frame}
        \frametitle{Additional Literature Research}
        \begin{itemize}
            \item 
        \end{itemize}
    \end{frame}
